---
title: "statistical analysis"
author: "Mingjia"
date: "3/8/2022"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(car)
library(rstatix)
library(dplyr)
library(tidyr)
contrast.default = options("contrasts")
options(contrasts = c("contr.helmert", "contr.poly"))
```

```{r}
library(data.table)
library(ggplot2)
library(dplyr)
library(purrr)
library(gridExtra)
source("utils.R")
# ---- Load the Data ----
data_subj = fread("summary data/test_accuracy.csv") 
```


```{r}
#------------------median split IDs-----------------------
data_subj_4cat = filter(data_subj, condition == "4cat")

below_4cat_idx = with(data_subj_4cat,order(train[condition == "4cat"]))[1:30]
below_4cat_ID = with(data_subj_4cat,ID[below_4cat_idx])
data_subj_4cat$medgrp = ifelse(data_subj_4cat$ID %in% below_4cat_ID,"below","above")

data_subj_2cat = filter(data_subj, condition == "2cat")

below_2cat_idx = with(data_subj_2cat,order(train[condition == "2cat"]))[1:30]
below_2cat_ID = with(data_subj_2cat,ID[below_2cat_idx])
data_subj_2cat$medgrp = ifelse(data_subj_2cat$ID %in% below_2cat_ID,"below","above")

data_subj = rbind(data_subj_2cat,data_subj_4cat)

```

# accuracy on training items
## ANOVA: conditions x accuracy group 
```{r}
res.aov <- anova_test(data=data_subj,train ~ condition * medgrp, 
                      type=3, effect.size = "pes",detailed=T)
get_anova_table(res.aov,correction = "none")
Prcorr_stats = data_subj %>% 
                  group_by(condition,medgrp) %>% 
                  summarize(mean = mean(train),
                            SD = sd(train),
                            SEM = SD/sqrt(length(train)))
show(Prcorr_stats)
```

## t-test: compare 2cat and 4cat conditions for above-median group
```{r}
Prcorr_above = filter(data_subj,medgrp == "above")

t.test(data = Prcorr_above, train ~ condition, var.equal = TRUE)
Prcorr_above_stats = Prcorr_above %>% 
                     group_by(condition) %>% 
                     summarize(mean = mean(train),
                               SEM = sd(train)/sqrt(length(train)))
show(Prcorr_above_stats)

```

## t-test: compare 2cat and 4cat conditions for below-median group
```{r}
Prcorr_below = filter(data_subj,medgrp == "below")

t.test(data = Prcorr_below, train ~ condition, var.equal = TRUE)
Prcorr_above_stats = Prcorr_below %>% 
                     group_by(condition) %>% 
                     summarize(mean = mean(train),
                               SEM = sd(train)/sqrt(length(train)))
show(Prcorr_above_stats)

```


# accuracy on critical items
## ANOVA: conditions x accuracy group 
```{r}
res.aov <- anova_test(data=data_subj,critical ~ condition * medgrp, 
                      type=3, effect.size = "pes",detailed=T)
get_anova_table(res.aov,correction = "none")
Prcorr_stats = data_subj %>% 
                  group_by(condition,medgrp) %>% 
                  summarize(mean = mean(critical),
                            SD = sd(critical),
                            SEM = SD/sqrt(length(critical)))
show(Prcorr_stats)
```

## t-test: compare 2cat and 4cat conditions for above-median group
```{r}
Prcorr_above = filter(data_subj,medgrp == "above")

t.test(data = Prcorr_above, critical ~ condition, var.equal = TRUE)
Prcorr_above_stats = Prcorr_above %>% 
                     group_by(condition) %>% 
                     summarize(mean = mean(critical),
                               SEM = sd(critical)/sqrt(length(critical)))
show(Prcorr_above_stats)

```

## t-test: compare 2cat and 4cat conditions for below-median group
```{r}
Prcorr_below = filter(data_subj,medgrp == "below")

t.test(data = Prcorr_below, critical ~ condition, var.equal = TRUE)
Prcorr_above_stats = Prcorr_below %>% 
                     group_by(condition) %>% 
                     summarize(mean = mean(critical),
                               SEM = sd(critical)/sqrt(length(critical)))
show(Prcorr_above_stats)

```


# accuracy on other transfer items
## ANOVA: conditions x accuracy group 
```{r}
res.aov <- anova_test(data=data_subj,other ~ condition * medgrp, 
                      type=3, effect.size = "pes",detailed=T)
get_anova_table(res.aov,correction = "none")
Prcorr_stats = data_subj %>% 
                  group_by(condition,medgrp) %>% 
                  summarize(mean = mean(critical),
                            SD = sd(critical),
                            SEM = SD/sqrt(length(critical)))
show(Prcorr_stats)
```

## t-test: compare 2cat and 4cat conditions for above-median group
```{r}
Prcorr_above = filter(data_subj,medgrp == "above")

t.test(data = Prcorr_above, other ~ condition, var.equal = TRUE)
Prcorr_above_stats = Prcorr_above %>% 
                     group_by(condition) %>% 
                     summarize(mean = mean(other),
                               SEM = sd(other)/sqrt(length(other)))
show(Prcorr_above_stats)

```

## t-test: compare 2cat and 4cat conditions for below-median group
```{r}
Prcorr_below = filter(data_subj,medgrp == "below")

t.test(data = Prcorr_below, other ~ condition, var.equal = TRUE)
Prcorr_above_stats = Prcorr_below %>% 
                     group_by(condition) %>% 
                     summarize(mean = mean(other),
                               SEM = sd(other)/sqrt(length(other)))
show(Prcorr_above_stats)

```